### 2019-08-21 paper/paper.tex
Simplified constraints section.

% - Abstract
% - Introduction
% - Problem Definition
%   - Optimization
%   - Parameterization
%   - Bounds
%   - Constraints
% - Solutions
%   - Parameters
%   - Eigenvalues
%   - HQM
% - Discussion and Conclusion

@@

\section*{Introduction}
%
We introduced a method of optimizing four geometric parameters of a bicycle's
design to minimize the so called Handling Quality Metric
(HQM)~\cite{Moore2016}. Here we expand that method to optimize all X geometric
and inertial parameters of the benchmark parameterimization of the linear
Whipple-Carvallo bicycle model under constraints that guarantee a physically
realizable bicycle. This improves over the prior work by expanding the search
space with many more parameters and the guarntee of realizability.

\section*{Problem Definition}
%
We search for 24 optimization variables that minimize the Handling Quality
Metric defined in~\cite{Hess2012}.

\subsection*{Bicycle Model Parameters}
%
Our problem formulation relies on a new parameterization that reflects both a
reformulation of and addition to the benchmark parameterization of the linear
Whipple-Carvallo bicycle model~\cite{Meijaard2007}. This parameterization
differs from the benchmark parameterization in that the person and rear frame
are treated as separate but fixed rigid bodies each with their on inertial
parameters and that the inertial parameters of all bodies are expressed in
terms of central principal radii of gyration so that the mass is decoupled from
the inertia. We also introduce two simple dimensional parameters that define
the geometric extents of the person. Table~\ref{tab:parameters} provides the
parameters and the initial values which are derived from the measurements of a
Batuvus Browser Bicycle and the rider, Jason, presented in~\cite{Moore2012}.
This allows the position and orientation of the rider to be specified
independtly of the rear frame but does not introduce any more than the
benchmark's four rigid bodies.

The variables are as follows:
%
\begin{itemize}
  \item wheelbase, trail, steer axis tilt, wheel radii
  \item somersault angle of the person (same direction as bicycle pitch)
  \item masses of the front frame, rear frame, front wheel, and rear wheel
  \item mass center locations of the front frame, rear frame, and rider
  \item principal central radii of gyration of front and rear frames
  \item principal inertia axis pitch angles of the front frame, rear frame, and rider
\end{itemize}

\begin{table}
  \caption{Parameters and their default values.}
  \begin{tabular}{llll}
    \toprule
    Variable & Value & Units & Description \\
    \midrule
    $c$ &  0.068581 & \si{\meter} & Trail \\
    $w$ &  1.1210 & \si{\meter} & Wheelbase \\
    $\lambda$ &  0.39968 & \si{\radian} & Steer axis tilt \\
    $g$ &  9.81 & \si{\meter\per\second\squared} & Acceleration due to gravity \\
    $v$ &  3.0 & \si{\meter\per\second} & Forward speed \\
    Rear Wheel [R] & & \\
    \midrule
    $m_R$ &  3.11 & \si{\kilogram} & mass \\
    $r_R$ &  0.34096 & \si{\meter} & Rear wheel radius \\
    $x_R$ & 0 & \si{\meter} & Rear wheel mass center \\
    $y_R$ & 0 & \si{\meter} & Rear wheel mass center \\
    $z_R$ & -0.34096 & \si{\meter} & Rear wheel mass center \\
    $k_{Raa}$ &  0.17050 & \si{\meter} & Rear wheel central principal radii of gyration \\
    $k_{Rbb}$ &  0.17050 & \si{\meter} & Rear wheel central principal radii of gyration  \\
    $k_{Ryy}$ &  0.22136 & \si{\meter} & Rear wheel central principal radii of gyration \\
    Front Wheel [F] & & \\
    \midrule
    $m_F$ &  2.02 & \si{\kilogram} & Mass \\
    $r_F$ &  0.34353 & \si{\meter} & Radius \\
    $x_F$ &  1.1210 & \si{\meter} & Mass center \\
    $y_F$ & 0.0 & \si{\meter} & Mass center \\
    $z_F$ & -0.34353 & \si{\meter} & Mass center \\
    $k_{Faa}$ &  0.20917 & \si{\meter} & Central principal radius of gyration \\
    $k_{Fbb}$ &  0.20917 & \si{\meter} & Central principal radius of gyration \\
    $k_{Fyy}$ &  0.27179 & \si{\meter} & Central principal radius of gyration \\
    Person [P] & & \\
    \midrule
    $l_P$ &  1.7280 & \si{\meter} & Body length \\
    $w_P$ &  0.48300 & \si{\meter} & Body width \\
    $m_P$ &  83.500 & \si{\kilogram} & Mass \\
    $x_P$ &  0.31577 & \si{\meter} & Mass center \\
    $y_P$ & 0.0 & \si{\meter} & Mass center \\
    $z_P$ & -1.0990 & \si{\meter} & Mass center \\
    $k_{Paa}$ &  0.36797 & \si{\meter} & Central principal radius of gyration \\
    $k_{Pbb}$ &  0.15276 & \si{\meter} & Central principal radius of gyration \\
    $k_{Pyy}$ &  0.36717 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_P$ & 0.18618 & \si{\radian} & Principal axis angle \\
    Front Frame [H] & & \\
    \midrule
    $m_H$ & 3.2200 & \si{\kilogram} & Mass \\
    $x_H$ & 0.86695 & \si{\meter} & Mass center \\
    $y_H$ & 0.0 & \si{\meter} & Mass center \\
    $z_H$ & -0.74824 & \si{\meter} & Mass center \\
    $k_{Haa}$ & 0.29556 & \si{\meter} & Central principal radius of gyration \\
    $k_{Hbb}$ & 0.14493 & \si{\meter} & Central principal radius of gyration \\
    $k_{Hyy}$ & 0.27630 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_H$ & 0.36995 & \si{\radian} & Principal axis angle \\
    Rear Frame [D] & & \\
    \midrule
    $m_D$ &  9.8600 & \si{\kilogram} & Mass \\
    $x_D$ &  0.27595 & \si{\meter} & Mass center \\
    $y_D$ & 0 & \si{\meter} & Mass center \\
    $z_D$ & -0.53784 & \si{\meter} & Mass center \\
    $k_{Daa}$ &  0.28587 & \si{\meter} & Central principal radius of gyration \\
    $k_{Dbb}$ &  0.22079 & \si{\meter} & Central principal radius of gyration \\
    $k_{Dyy}$ &  0.36539 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_D$ &  1.1722 & \si{\radian} & Principal axis angle \\
    \bottomrule
  \end{tabular}
\end{table}

$\mathbf{p}\in\mathbb{R}^{24}$These parameters can be transformed into the benchmark parameterization
r adily, but not vice versa.
We search for the optimal values of a subset of 23 of the principal parameters.

\begin{align}
  \mathbf{p} = &
    [w \quad
     c \quad
     \lambda \quad
     m_D \quad
     x_D \quad
     z_D \quad
     k_{Daa} \quad
     k_{Dbb} \quad
     \alpha_D \quad
     x_P \quad
     z_P \quad
     \alpha_P \quad \\
 &    m_H \quad
     x_H \quad
     z_H \quad
     k_{Haa} \quad
     k_{Hbb} \quad
     k_{Hyy} \quad
     \alpha_H \quad
     r_R \quad
     m_R \quad
     r_F \quad
     m_F]
\end{align}

\subsection*{Bounds and Constraints}
%
The optimal principal parameters are subject to a set of constraints designed
to ensure a physically realizable bicycle is obtained.
We formulate bounds on the variables as well as equality and inequality
constraints among the variables to ensure a physically realizable bicycle.
Below the constraints are defined and grouped by the associated rigid body or
collection thereof:
%
\begin{description}
  \item[Vehicle] The resulting combination of the five rigid bodies.
    \begin{itemize}
      \itemsep0em
      \item The physical extents of the bicycle and rider must exist above the
        ground plane.
      \item Both bicycle and rider are symmetric about the sagittal
        plane.
      \item The mass of each bicycle rigid body is positive, greater than a
        minimum value, and the total mass is below a reasonably lift-able
        amount.
      \item The wheels cannot overlap, i.e. wheelbase > front radius + rear
        radius.
      \item The bicycle cannot topple forward during hard braking or backward
        during hard acceleration, i.e. -1 g < acceleration < 1 g.
    \end{itemize}

@@

\section*{Rigid Body Definitions}

\subsection*{Rear Frame [D]}
%
There are five free parameters associated with the rear frame's inertial
characteristics:

\begin{description}
  \item[$m_D$] Mass of the rear frame.
  \item[$x_D$] Location along the $X$ axis of the rear frame center of mass.
  \item[$z_D$] Location along the $Z$ axis of the rear frame center of mass.
  \item[$k_{Daa}$] Maximum principal central radius of gyration in the $XZ$
    plane.
  \item[$k_{Dbb}$] Minimum principal central radius of gyration in the $XZ$
    plane.
  \item[$\alpha_D$] Angle between the $X$ axis and the maximum principal axis
    that lies in the $XZ$ plane.
\end{description}

Several constraints are set for the rear frame. We constrain the rear frame to
be planar, $g_1$ and symmetric with respect to the $XZ$ plane, i.e. $I_{Dxy} =
I_{Dyz} = 0$. We prevent the rear frame from penetrating the ground by limiting
the inertial spread with respect to its mass center, $c_{12}$, but also set a
minimum inertial spread to ensure a frame can span from the rear wheel to the
mass center of the rear frame, $c_9$. The spread factor in $c_{12}$ of 1.4 is
based on the ratio of geometrical spread of a typical bicycle frame and its
radius of gyration. Several parameters are bounded. We require the rear frame
mass to be positive, the center of mass not penetrate the ground, and we allow
for any angular orientation of the $XZ$ principal directions but limit the
angle to $-\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2}$.

@@

We assume that the person's joint configurations are such that they are in a
nominal configuration for pedaling, i.e. an average normal everyday riding
position on a typical bicycle. The person is assumed to be symmetric about the
$XZ$ plane. We allow the rider to be rotated about the $Y$ axis and positioned
anywhere within the plane of symmetry above the ground. Three free parameters
are associated with these assumptions:

\begin{description}
  \item[$m_P$] The mass of the person which is fixed at $XX \si{kg}$.
  \item[$k_{Pxx}$] Central radius of gyration with respect to the $X$ axis
    where $I_{Pxx} = m_P k_{Pxx}^2$.
  \item[$k_{Pyy}$] Central radius of gyration with respect to the $Y$ axis
    where $I_{Pyy} = m_P k_{Pyy}^2=$.
  \item[$k_{Pzz}$] Central radius of gyration with respect to the $Z$ axis
    where $I_{Pzz} = m_P k_{Pzz}^2=$.
  \item[$I_{Bxy}, I_{Byz}$] Products of inertia are zero.
  \item[$y_P$] Is zero.
\end{description}

@@

The front frame is symmetric about the $XZ$ plane so $I_{Hxy}, I_{Hyz} = 0$.
There are seven free parameters:

@@

We allow for any angular orientation of the $XZ$ principal directions but limit
the angle to $-\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2}$.  We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{13}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_8$. The spread factor in $c_{13}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration. The
front frame is not planar but is narrow with respect to the $XZ$ plane, which
is enforced by constraint $c_1$.

We enforce the assumption that both wheels have moments of inertia of that of a
simple ring, $g_2 \ldots g_7$ and that mass and radius should be greater than
some minimal size based on small bicycle wheel.

\subsubsection{Parameters}

@@

\subsubsection{Bounds}

The trail can take on any real value as well as the steer axis tilt except the
bound the angle to a minimal range:

\begin{align}
  -\frac{\pi}{2} \leq \lambda \leq \frac{\pi}{2}
\end{align}

\subsubsection{Constraints}

We introduce a constraint $c_{10}$ that prevents the wheels from physically
overlapping and require that the bicycle be liftable by an average person,
$c_{11}$. Finally, we require that the bicycle not topple forward during hard
breaking or backward during hard acceleration.

This translates to two constraints, $c_6,c_7$ that bound the total center of
mass $(x_T,z_T)$ in a triangle in the $XZ$ plane.

Lastly, we constrain the eight closed loop eigenvalues associated with the
controller in ~\cite{Hess2012} to be stable, i.e. have negative real parts.
These are expressed in constraints $c_{14},\ldots,c_{21}$. Closed loop
stability is required for the HQM to provide a meaningful result.

\subsection{Summary}

>>>>

% - Abstract
% - Introduction
% - Problem Definition
%   - Parameterization
%   - Bounds and Constraints
%   - Free Parameters
%   - Optimization
% - Solutions
%   - Parameters
%   - Eigenvalues
%   - HQM
% - Discussion and Conclusion

@@

\section{Introduction}
%
We introduced a method of optimizing four geometric parameters of a bicycle's
design to minimize the so called Handling Quality Metric
(HQM)~\cite{Moore2016}. Here we expand that method to optimize all X geometric
and inertial parameters of the benchmark parameterimization of the linear
Whipple-Carvallo bicycle model under constraints that guarantee a physically
realizable bicycle. This improves over the prior work by expanding the search
space with many more parameters and the guarntee of realizability.

\section{Problem Definition}
%
We search for 24 optimization variables that minimize the Handling Quality
Metric defined in~\cite{Hess2012}.

\subsection{Bicycle Model Parameters}
%
Our problem formulation relies on a new parameterization that reflects both a
reformulation of and addition to the benchmark parameterization of the linear
Whipple-Carvallo bicycle model~\cite{Meijaard2007}. This parameterization
differs from the benchmark parameterization in that the person and rear frame
are treated as separate but fixed rigid bodies each with their on inertial
parameters and that the inertial parameters of all bodies are expressed in
terms of central principal radii of gyration so that the mass is decoupled from
the inertia. We also introduce two simple dimensional parameters that define
the geometric extents of the person. Table~\ref{tab:parameters} provides the
parameters and the initial values which are derived from the measurements of a
Batuvus Browser Bicycle and the rider, Jason, presented in~\cite{Moore2012}.
This allows the position and orientation of the rider to be specified
independtly of the rear frame but does not introduce any more than the
benchmark's four rigid bodies.
%
\begin{table}
  \caption{Full set of 47 parameters and their default values derived from the
  measurements in~\cite{Moore2012}.}
  \label{tab:parameters}
  \begin{tabular}{llll}
    \toprule
    Variable & Value & Units & Description \\
    \midrule
    $c$ &  0.068581 & \si{\meter} & Trail \\
    $w$ &  1.1210 & \si{\meter} & Wheelbase \\
    $\lambda$ &  0.39968 & \si{\radian} & Steer axis tilt \\
    $g$ &  9.81 & \si{\meter\per\second\squared} & Acceleration due to gravity \\
    $v$ &  3.0 & \si{\meter\per\second} & Forward speed \\
    Rear Wheel [R] & & \\
    \midrule
    $m_R$ &  3.11 & \si{\kilogram} & mass \\
    $r_R$ &  0.34096 & \si{\meter} & Rear wheel radius \\
    $x_R$ & 0 & \si{\meter} & Rear wheel mass center \\
    $y_R$ & 0 & \si{\meter} & Rear wheel mass center \\
    $z_R$ & -0.34096 & \si{\meter} & Rear wheel mass center \\
    $k_{Raa}$ &  0.17050 & \si{\meter} & Rear wheel central principal radii of gyration \\
    $k_{Rbb}$ &  0.17050 & \si{\meter} & Rear wheel central principal radii of gyration  \\
    $k_{Ryy}$ &  0.22136 & \si{\meter} & Rear wheel central principal radii of gyration \\
    Front Wheel [F] & & \\
    \midrule
    $m_F$ &  2.02 & \si{\kilogram} & Mass \\
    $r_F$ &  0.34353 & \si{\meter} & Radius \\
    $x_F$ &  1.1210 & \si{\meter} & Mass center \\
    $y_F$ & 0.0 & \si{\meter} & Mass center \\
    $z_F$ & -0.34353 & \si{\meter} & Mass center \\
    $k_{Faa}$ &  0.20917 & \si{\meter} & Central principal radius of gyration \\
    $k_{Fbb}$ &  0.20917 & \si{\meter} & Central principal radius of gyration \\
    $k_{Fyy}$ &  0.27179 & \si{\meter} & Central principal radius of gyration \\
    Person [P] & & \\
    \midrule
    $l_P$ &  1.7280 & \si{\meter} & Body length \\
    $w_P$ &  0.48300 & \si{\meter} & Body width \\
    $m_P$ &  83.500 & \si{\kilogram} & Mass \\
    $x_P$ &  0.31577 & \si{\meter} & Mass center \\
    $y_P$ & 0.0 & \si{\meter} & Mass center \\
    $z_P$ & -1.0990 & \si{\meter} & Mass center \\
    $k_{Paa}$ &  0.36797 & \si{\meter} & Central principal radius of gyration \\
    $k_{Pbb}$ &  0.15276 & \si{\meter} & Central principal radius of gyration \\
    $k_{Pyy}$ &  0.36717 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_P$ & 0.18618 & \si{\radian} & Principal axis angle \\
    Front Frame [H] & & \\
    \midrule
    $m_H$ & 3.2200 & \si{\kilogram} & Mass \\
    $x_H$ & 0.86695 & \si{\meter} & Mass center \\
    $y_H$ & 0.0 & \si{\meter} & Mass center \\
    $z_H$ & -0.74824 & \si{\meter} & Mass center \\
    $k_{Haa}$ & 0.29556 & \si{\meter} & Central principal radius of gyration \\
    $k_{Hbb}$ & 0.14493 & \si{\meter} & Central principal radius of gyration \\
    $k_{Hyy}$ & 0.27630 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_H$ & 0.36995 & \si{\radian} & Principal axis angle \\
    Rear Frame [D] & & \\
    \midrule
    $m_D$ &  9.8600 & \si{\kilogram} & Mass \\
    $x_D$ &  0.27595 & \si{\meter} & Mass center \\
    $y_D$ & 0 & \si{\meter} & Mass center \\
    $z_D$ & -0.53784 & \si{\meter} & Mass center \\
    $k_{Daa}$ &  0.28587 & \si{\meter} & Central principal radius of gyration \\
    $k_{Dbb}$ &  0.22079 & \si{\meter} & Central principal radius of gyration \\
    $k_{Dyy}$ &  0.36539 & \si{\meter} & Central principal radius of gyration \\
    $\alpha_D$ &  1.1722 & \si{\radian} & Principal axis angle \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Bounds and Constraints}
%
The optimal principal parameters are subject to a set of constraints designed
to ensure a physically realizable bicycle is obtained. We formulate bounds on
the variables as well as equality and inequality constraints among the
variables to ensure a physically realizable bicycle. Below the constraints are
defined and grouped by the associated rigid body or collection thereof:
%
\begin{description}
  \item[Vehicle] The resulting combination of the five rigid bodies.
    \begin{itemize}
      \itemsep0em
      \item The physical extents of the bicycle and rider must exist above the
        ground plane.
      \item Both bicycle and rider are symmetric about the sagittal
        plane.
      \item The mass of each bicycle rigid body is positive, greater than a
        minimum value, and the total mass is below a reasonably lift-able
        amount.
      \item The wheels cannot overlap, i.e. wheelbase > front radius + rear
        radius.
      \item The bicycle cannot topple forward during hard braking or backward
        during hard acceleration, i.e. -1 g < acceleration < 1 g.
    \end{itemize}

@@

\subsection*{Rear Frame [D]}
%
Several constraints are set for the rear frame. We constrain the rear frame to
be planar, $g_1$, and symmetric with respect to the $XZ$ plane. We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{12}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_9$. The spread factor in $c_{12}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration.
Several parameters are bounded. We require the rear frame mass to be positive,
the center of mass not penetrate the ground, and we allow for any angular
orientation of the $XZ$ principal directions but limit the angle to
$-\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2}$ as angle beyond that are
redundant.

@@

We assume that the person's joint configurations are such that they are in a
nominal configuration for pedaling, i.e. an average normal everyday riding
position on a typical bicycle, i.e. they stayed in the same configuration as
they were seated on the Batavus Browser bicycle. The person is assumed to be
symmetric about the $XZ$ plane. We allow the rider to be rotated about the $Y$
axis and positioned anywhere within the plane of symmetry above the ground.

@@

The front frame is symmetric about the $XZ$ plane so $I_{Hxy}, I_{Hyz} = 0$. We
allow for any angular orientation of the $XZ$ principal directions but limit
the angle to $-\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2}$.  We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{13}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_8$. The spread factor in $c_{13}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration. The
front frame is not planar but is narrow with respect to the $XZ$ plane, which
is enforced by constraint $c_1$.

We enforce the assumption that both wheels have moments of inertia of that of a
simple ring, $g_2 \ldots g_7$ and that mass and radius should be greater than a
minimal size based on small purchable spoked wheel with tire.

The trail and wheelbase can take on any real values. The steer axis tilt is
limted to 180 degrees. We introduce a constraint $c_{10}$ that prevents the
wheels from physically overlapping and require that the bicycle be liftable by
an average person, $c_{11}$. Finally, we require that the bicycle not topple
forward during hard breaking or backward during hard acceleration.

This translates to two constraints, $c_6,c_7$ that bound the total center of
mass $(x_T,z_T)$ in a triangle in the $XZ$ plane. Lastly, we constrain the
eight closed loop eigenvalues associated with the controller in
~\cite{Hess2012} to be stable, i.e. have negative real parts.  These are
expressed in constraints $c_{14},\ldots,c_{21}$. Closed loop stability is
required for the HQM to provide a meaningful result.

\subsection{Free parameters}
%
These constraints leave 23 free parameters for the optimizer to These
parameters can be transformed into the benchmark parameterization r adily, but
not vice versa.
We search for the optimal values of a subset of 23 of the principal parameters.

$\mathbf{p}\in\mathbb{R}^{23}$

There are five free parameters associated with the rear frame's inertial
characteristics:

\begin{description}
  \item[$m_D$] Mass of the rear frame.
  \item[$x_D$] Location along the $X$ axis of the rear frame center of mass.
  \item[$z_D$] Location along the $Z$ axis of the rear frame center of mass.
  \item[$k_{Daa}$] Maximum principal central radius of gyration in the $XZ$
    plane.
  \item[$k_{Dbb}$] Minimum principal central radius of gyration in the $XZ$
    plane.
  \item[$\alpha_D$] Angle between the $X$ axis and the maximum principal axis
    that lies in the $XZ$ plane.
\end{description}
 Three free parameters
are associated with these assumptions:

There are seven free parameters:

@@

@@

\begin{align}
  \begin{split}
    \mathbf{p} = [ &
       w        \quad
       c        \quad
       \lambda  \quad
       m_D      \quad
       x_D      \quad
       z_D      \quad
       k_{Daa}  \quad
       k_{Dbb}  \quad
       \alpha_D \quad
       x_P      \quad
       z_P      \quad
       \alpha_P \\
     & m_H      \quad
       x_H      \quad
       z_H      \quad
       k_{Haa}  \quad
       k_{Hbb}  \quad
       k_{Hyy}  \quad
       \alpha_H \quad
       r_R      \quad
       m_R      \quad
       r_F      \quad
       m_F]
  \end{split}
\end{align}

\begin{description}
  \item[$m_P$] The mass of the person which is fixed at $XX \si{kg}$.
  \item[$k_{Pxx}$] Central radius of gyration with respect to the $X$ axis
    where $I_{Pxx} = m_P k_{Pxx}^2$.
  \item[$k_{Pyy}$] Central radius of gyration with respect to the $Y$ axis
    where $I_{Pyy} = m_P k_{Pyy}^2=$.
  \item[$k_{Pzz}$] Central radius of gyration with respect to the $Z$ axis
    where $I_{Pzz} = m_P k_{Pzz}^2=$.
  \item[$I_{Bxy}, I_{Byz}$] Products of inertia are zero.
  \item[$y_P$] Is zero.
\end{description}
\subsection{Summary}
